Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-22 Paper.tex
Nick's corrections.
More discussion

Thus we may define a world-state collapse function $L_S$:
\begin{eqnarray}
L_S(\boldsymbol{\sigma}) & \equiv & \{ p(a): \boldsymbol{\sigma}[a] \neq \varnothing \} \\
p(a) & \equiv & \big(a, \texttt{\small RLP}\big( (\boldsymbol{\sigma}[a]_n, \boldsymbol{\sigma}[a]_b, \boldsymbol{\sigma}[a]_s, \boldsymbol{\sigma}[a]_c) \big) \big)
\end{eqnarray}

This function, $L_S$, is used alongside the trie function to provide a short identity (hash) of the world state. We assume:
\begin{equation}
\forall a: \boldsymbol{\sigma}[a] = \varnothing \; \vee \; (a \in \mathbb{B}_{20} \; \wedge \; v(\boldsymbol{\sigma}[a]))
\end{equation}

Where $v$ is the account validity function:
\begin{eqnarray}
\quad v(x) & \equiv & x_n \in \mathbb{P} \wedge x_p \in \mathbb{P} \wedge (x_r = x_c = \varnothing \vee w(x)) \\
\quad w(x) & \equiv & x_r \in \mathbb{B}_{32} \quad \wedge \quad x_c \in \mathbb{B}_{32}
\end{eqnarray}

@@

\subsection{Data Feeds}

External server runs node. Creates \& signs a transaction every minute containing new data. Sends to contract which knows to accept data only from this address. Allows polling of data from all other contracts (possibly for a microfee).

\subsection{Random Numbers}

Hash the block timestamp; for a series of pseudorandoms, take the previous, add some constant and hash the result.

For a more secure pseudo-random offering both parties agree on a number of random data feed contracts; these are concatenated along with the block timestamp and hashed to produce the first number in the series.

>>>>

Thus we may define a world-state collapse function $L_S$:
\begin{equation}
L_S(\boldsymbol{\sigma}) \equiv \{ p(a): \boldsymbol{\sigma}[a] \neq \varnothing \}
\end{equation}
where
\begin{equation}
p(a) \equiv \begin{cases}
\big(a, \texttt{\small RLP}\big( (\boldsymbol{\sigma}[a]_n, \boldsymbol{\sigma}[a]_b) \big) \big) & \text{if} \; \boldsymbol{\sigma}[a]_s = \varnothing\\
\big(a, \texttt{\small RLP}\big( (\boldsymbol{\sigma}[a]_n, \boldsymbol{\sigma}[a]_b, \boldsymbol{\sigma}[a]_s, \boldsymbol{\sigma}[a]_c) \big) \big) & \text{otherwise}
\end{cases}
\end{equation}
This function, $L_S$, is used alongside the trie function to provide a short identity (hash) of the world state. We assume:
\begin{equation}
\forall a: \boldsymbol{\sigma}[a] = \varnothing \; \vee \; (a \in \mathbb{B}_{20} \; \wedge \; v(\boldsymbol{\sigma}[a]))
\end{equation}

Where $v$ is the account validity function:
\begin{eqnarray}
\quad v(x) & \equiv & x_n \in \mathbb{P} \wedge x_b \in \mathbb{P} \wedge (x_s = x_c = \varnothing \vee w(x)) \\
\quad w(x) & \equiv & x_s \in \mathbb{B}_{32} \quad \wedge \quad x_c \in \mathbb{B}_{32}
\end{eqnarray}

@@

There are several patterns of contracts engineering that allow particular useful behaviours; two of these that I will briefly discuss are data feeds and random numbers.

\subsection{Data Feeds}
A data feed contract is one which provides a single service: it gives access to information from the external world within Ethereum. The accuracy and timeliness of this information is not guaranteed and it is the task of a secondary contract author---the contract that utilises the data feed---to determine how much trust can be placed in any single data feed.

The general pattern involves a single contract within Ethereum which, when given a message call, replies with some timely information concerning an external phenomenon. An example might be the local temperature of New York City. This would be implemented as a contract that returned that value of some known point in storage. Of course this point in storage must be maintained with the correct such temperature, and thus the second part of the pattern would be for an external server to run an Ethereum node, and immediately on discovery of a new block, creates a new valid transaction, sent to the contract, updating said value in storage. The contract's code would accept such updates only from the identity contained on said server.

\subsection{Random Numbers}
Providing random numbers within a deterministic system is, naturally, an impossible task. However, we can approximate with pseudo-random numbers by utilising data which is generally unknowable at the time of transacting. Such data might include the block's hash, the block's timestamp and the block's coinbase address. For a series of such numbers, a trivial solution would be to work from the previous pseudo-random number, adding some constant amount and hashing the result.

This strategy does have a downside: a miner with sufficient power could alter any of the above values in order to deliver a seed in order to alter the outcome of the pseudorandom-based executions. For a more secure pseudo-random offering, all involved parties could agree on a number of data feed contracts; these could be combined along with the block timestamp and hashed to produce the first number in the series. By spreading the inputs and thus the trust between numerous parties the likelihood of a malicious miner altering the outcome becomes increasingly less likely.
